Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/introduction.tex
intro and rel work

There exist many sources of unstructured data that have been partially or
completely categorized by human editors.  In this paper we focus on
unstructured text data that has been, at least in part, manually
categorized.  Examples include but are not limited to webpages and curated
hierarchical directories of the same \citep{DMOZ}, product descriptions and
catalogs, %(e.g.~\citep{AMAZON} as available from \citep{SNAP})
and patient records %hospital treatment transcripts
and diagnosis codes assigned to them for bookkeeping and insurance purposes
(e.g.~hospital discharge summaries with 
International Classification of Disease 9th Revision, Clinical Modification
(ICD-9-CM) codes assigned \cite{ICD9}).  In this work we show how to combine
these two sources of information using a single model that allows one to
categorize new text documents automatically, suggest labels that might be
inaccurate, compute improved similarities between documents for information
retrieval purposes, and more. The models and techniques that we develop in
this paper are applicable in other data as well, namely, any unstructured
representations of data that have been hierarchically classified (e.g.,~image
catalogs with bag-of-feature image representations).

@@

%The task of multi-label classification, selecting the k-best labels for a given
%instance, has been a topic of research for several years. One simplistic way to
%carry out the classification is through a series of independent binary
%classifiers, but this ignores the many inherent dependencies among the
%labels. Thus, much work has been devoted on incorporating the co-occurence
%patterns of the labels into the classification task.

>>>>

There exist many sources of unstructured data that have been partially or
completely categorized by human editors.  In this paper we focus on
unstructured text data that has been, at least in part, manually
categorized.  Examples include but are not limited to webpages and curated
hierarchical directories of the same \citep{DMOZ}, product descriptions and
catalogs, %(e.g.~\citep{AMAZON} as available from \citep{SNAP})
and patient records %hospital treatment transcripts
and diagnosis codes assigned to them for bookkeeping and insurance purposes.
In this work we show how to combine 
these two sources of information using a single model that allows one to
categorize new text documents automatically, suggest labels that might be
inaccurate, compute improved similarities between documents for information
retrieval purposes, and more. The models and techniques that we develop in
this paper are applicable to other data as well, namely, any unstructured
representations of data that have been hierarchically classified (e.g.,~image
catalogs with bag-of-feature image representations).

@@
